Characterization and evolution of hourly extreme precipitation in France using an Explicit-Convection Regional Climate Model

### 2025-11-24 article/fig7.qmd
Initial commit: src, article, outputs, outputs_nr10

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=4pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \input{macros_fig7.tex}
---

@@

trend_pluie_fev = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/fev/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/fev/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_fev.svg"
)
trend_pluie_mar = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/mar/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/mar/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_mar.svg"
)
trend_pluie_jui = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/jui/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/jui/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_jui.svg"
)
trend_pluie_nov = assemble(
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/nov/mod_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/nov/obs_signif_norast.svg",
  "../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
  "figures/trend_horaire_pluie_nov.svg"
)
df_trend_pluie_fev = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "fev") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_mar = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "mar") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_jui = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "jui") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
df_trend_pluie_nov = combined_all.loc[(combined_all["echelle"] == "horaire") & (combined_all["season"] == "nov") & (combined_all["col_calculate"] == "z_T_p_signif"), ["n", "r", "me", "delta"]]
```

@@

# Récupération des valeurs mois par mois (échelle horaire)
r_fev, n_fev, me_fev = _first_vals(df_trend_pluie_fev)
r_mar, n_mar, me_mar = _first_vals(df_trend_pluie_mar)
r_jun, n_jun, me_jun = _first_vals(df_trend_pluie_jui)   # jui -> JUN
r_nov, n_nov, me_nov = _first_vals(df_trend_pluie_nov)

# Génération des macros LaTeX
macros = rf"""
\newcommand{{\rFEB}}{{{r_fev:.2f}}}
\newcommand{{\nFEB}}{{{n_fev:d}}}
\newcommand{{\meFEB}}{{{me_fev:+.2f}}}

\newcommand{{\rMAR}}{{{r_mar:.2f}}}
\newcommand{{\nMAR}}{{{n_mar:d}}}
\newcommand{{\meMAR}}{{{me_mar:+.2f}}}

\newcommand{{\rJUN}}{{{r_jun:.2f}}}
\newcommand{{\nJUN}}{{{n_jun:d}}}
\newcommand{{\meJUN}}{{{me_jun:+.2f}}}

\newcommand{{\rNOV}}{{{r_nov:.2f}}}
\newcommand{{\nNOV}}{{{n_nov:d}}}
\newcommand{{\meNOV}}{{{me_nov:+.2f}}}
"""
with open("macros_fig7.tex", "w", encoding="utf-8") as f:
    f.write(macros)
```

@@

  \begin{tabularx}{\paperwidth}{
    >{\centering\arraybackslash}m{0.49\paperwidth}
    >{\centering\arraybackslash}m{0.49\paperwidth}
  }

    % --- Ligne 1 ---
    \textbf{\small FEB} & \textbf{\small MAR} \\[-0.5mm]
    \small $r=\ \rFEB$ \ (n=\ \nFEB) & \small $r=\ \rMAR$ \ (n=\ \nMAR) \\[-0.5mm]
    \small $ME=\ \meFEB\%$ & \small $ME=\ \meMAR\%$ \\[-0.5mm]
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_fev.pdf} &
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_mar.pdf} \\

    % --- Ligne 2 ---
    \textbf{\small JUN} & \textbf{\small NOV} \\[-0.5mm]
    \small $r=\ \rJUN$ \ (n=\ \nJUN) & \small $r=\ \rNOV$ \ (n=\ \nNOV) \\[-0.5mm]
    \small $ME=\ \meJUN\%$ & \small $ME=\ \meNOV\%$ \\[-0.5mm]
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_jui.pdf} &
    \includegraphics[width=\linewidth]{figures/trend_horaire_pluie_nov.pdf} \\

    % --- Ligne 3 ---
    \mbox{} &
    \begin{minipage}[c]{\linewidth}
      \centering
      \includegraphics[width=0.85\linewidth,keepaspectratio]{../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_horiz_signif.pdf}
      \makebox[0.85\linewidth][c]{\small \%}
    \end{minipage}
    \\

>>>>

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=0pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \usepackage[export]{adjustbox}
  - \input{macros_fig7.tex}
---

@@

trend_pluie_jan = assemble(
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/jan/mod_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/jan/obs_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
"figures/trend_horaire_pluie_jan.svg",
)
trend_pluie_fev = assemble(
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/fev/mod_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/fev/obs_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
"figures/trend_horaire_pluie_fev.svg",
)
trend_pluie_mar = assemble(
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/mar/mod_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/mar/obs_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
"figures/trend_horaire_pluie_mar.svg",
)
trend_pluie_avr = assemble(
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/avr/mod_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/avr/obs_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
"figures/trend_horaire_pluie_avr.svg",
)
trend_pluie_mai = assemble(
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/mai/mod_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/mai/obs_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
"figures/trend_horaire_pluie_mai.svg",
)
trend_pluie_jui = assemble( # Juin, fichier FR "jui"
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/jui/mod_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/jui/obs_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
"figures/trend_horaire_pluie_jui.svg",
)
trend_pluie_juill = assemble(
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/juill/mod_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/juill/obs_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
"figures/trend_horaire_pluie_juill.svg",
)
trend_pluie_aou = assemble(
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/aou/mod_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/aou/obs_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
"figures/trend_horaire_pluie_aou.svg",
)
trend_pluie_sep = assemble(
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/sep/mod_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/sep/obs_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
"figures/trend_horaire_pluie_sep.svg",
)
trend_pluie_oct = assemble(
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/oct/mod_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/oct/obs_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
"figures/trend_horaire_pluie_oct.svg",
)
trend_pluie_nov = assemble(
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/nov/mod_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/nov/obs_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
"figures/trend_horaire_pluie_nov.svg",
)
trend_pluie_dec = assemble(
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/dec/mod_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/dec/obs_signif_norast.svg",
"../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_signif.svg",
"figures/trend_horaire_pluie_dec.svg",
)
df_trend_pluie_jan = combined_all.loc[
(combined_all["echelle"] == "horaire")
& (combined_all["season"] == "jan")
& (combined_all["col_calculate"] == "z_T_p_signif"),
["n", "r", "me", "delta"],
]
df_trend_pluie_fev = combined_all.loc[
(combined_all["echelle"] == "horaire")
& (combined_all["season"] == "fev")
& (combined_all["col_calculate"] == "z_T_p_signif"),
["n", "r", "me", "delta"],
]
df_trend_pluie_mar = combined_all.loc[
(combined_all["echelle"] == "horaire")
& (combined_all["season"] == "mar")
& (combined_all["col_calculate"] == "z_T_p_signif"),
["n", "r", "me", "delta"],
]
df_trend_pluie_avr = combined_all.loc[
(combined_all["echelle"] == "horaire")
& (combined_all["season"] == "avr")
& (combined_all["col_calculate"] == "z_T_p_signif"),
["n", "r", "me", "delta"],
]
df_trend_pluie_mai = combined_all.loc[
(combined_all["echelle"] == "horaire")
& (combined_all["season"] == "mai")
& (combined_all["col_calculate"] == "z_T_p_signif"),
["n", "r", "me", "delta"],
]
df_trend_pluie_jui = combined_all.loc[
(combined_all["echelle"] == "horaire")
& (combined_all["season"] == "jui")
& (combined_all["col_calculate"] == "z_T_p_signif"),
["n", "r", "me", "delta"],
]
df_trend_pluie_juill = combined_all.loc[
(combined_all["echelle"] == "horaire")
& (combined_all["season"] == "juill")
& (combined_all["col_calculate"] == "z_T_p_signif"),
["n", "r", "me", "delta"],
]
df_trend_pluie_aou = combined_all.loc[
(combined_all["echelle"] == "horaire")
& (combined_all["season"] == "aou")
& (combined_all["col_calculate"] == "z_T_p_signif"),
["n", "r", "me", "delta"],
]
df_trend_pluie_sep = combined_all.loc[
(combined_all["echelle"] == "horaire")
& (combined_all["season"] == "sep")
& (combined_all["col_calculate"] == "z_T_p_signif"),
["n", "r", "me", "delta"],
]
df_trend_pluie_oct = combined_all.loc[
(combined_all["echelle"] == "horaire")
& (combined_all["season"] == "oct")
& (combined_all["col_calculate"] == "z_T_p_signif"),
["n", "r", "me", "delta"],
]
df_trend_pluie_nov = combined_all.loc[
(combined_all["echelle"] == "horaire")
& (combined_all["season"] == "nov")
& (combined_all["col_calculate"] == "z_T_p_signif"),
["n", "r", "me", "delta"],
]
df_trend_pluie_dec = combined_all.loc[
(combined_all["echelle"] == "horaire")
& (combined_all["season"] == "dec")
& (combined_all["col_calculate"] == "z_T_p_signif"),
["n", "r", "me", "delta"],
]
```

@@

# Récupération des valeurs mois par mois (échelle horaire)
r_jan, n_jan, me_jan = _first_vals(df_trend_pluie_jan)
r_fev, n_fev, me_fev = _first_vals(df_trend_pluie_fev)
r_mar, n_mar, me_mar = _first_vals(df_trend_pluie_mar)
r_avr, n_avr, me_avr = _first_vals(df_trend_pluie_avr)
r_mai, n_mai, me_mai = _first_vals(df_trend_pluie_mai)
r_jun, n_jun, me_jun = _first_vals(df_trend_pluie_jui) # jui -> JUN
r_jul, n_jul, me_jul = _first_vals(df_trend_pluie_juill) # juill -> JUL
r_aug, n_aug, me_aug = _first_vals(df_trend_pluie_aou) # aou -> AUG
r_sep, n_sep, me_sep = _first_vals(df_trend_pluie_sep)
r_oct, n_oct, me_oct = _first_vals(df_trend_pluie_oct)
r_nov, n_nov, me_nov = _first_vals(df_trend_pluie_nov)
r_dec, n_dec, me_dec = _first_vals(df_trend_pluie_dec)

# Génération des macros LaTeX
macros = rf"""
\newcommand{{\rJAN}}{{{r_jan:.2f}}}
\newcommand{{\nJAN}}{{{n_jan}}}
\newcommand{{\meJAN}}{{{me_jan:+.2f}}}

\newcommand{{\rFEB}}{{{r_fev:.2f}}}
\newcommand{{\nFEB}}{{{n_fev}}}
\newcommand{{\meFEB}}{{{me_fev:+.2f}}}

\newcommand{{\rMAR}}{{{r_mar:.2f}}}
\newcommand{{\nMAR}}{{{n_mar}}}
\newcommand{{\meMAR}}{{{me_mar:+.2f}}}

\newcommand{{\rAPR}}{{{r_avr:.2f}}}
\newcommand{{\nAPR}}{{{n_avr}}}
\newcommand{{\meAPR}}{{{me_avr:+.2f}}}

\newcommand{{\rMAY}}{{{r_mai:.2f}}}
\newcommand{{\nMAY}}{{{n_mai}}}
\newcommand{{\meMAY}}{{{me_mai:+.2f}}}

\newcommand{{\rJUN}}{{{r_jun:.2f}}}
\newcommand{{\nJUN}}{{{n_jun}}}
\newcommand{{\meJUN}}{{{me_jun:+.2f}}}

\newcommand{{\rJUL}}{{{r_jul:.2f}}}
\newcommand{{\nJUL}}{{{n_jul}}}
\newcommand{{\meJUL}}{{{me_jul:+.2f}}}

\newcommand{{\rAUG}}{{{r_aug:.2f}}}
\newcommand{{\nAUG}}{{{n_aug}}}
\newcommand{{\meAUG}}{{{me_aug:+.2f}}}

\newcommand{{\rSEP}}{{{r_sep:.2f}}}
\newcommand{{\nSEP}}{{{n_sep}}}
\newcommand{{\meSEP}}{{{me_sep:+.2f}}}

\newcommand{{\rOCT}}{{{r_oct:.2f}}}
\newcommand{{\nOCT}}{{{n_oct}}}
\newcommand{{\meOCT}}{{{me_oct:+.2f}}}

\newcommand{{\rNOV}}{{{r_nov:.2f}}}
\newcommand{{\nNOV}}{{{n_nov}}}
\newcommand{{\meNOV}}{{{me_nov:+.2f}}}

\newcommand{{\rDEC}}{{{r_dec:.2f}}}
\newcommand{{\nDEC}}{{{n_dec}}}
\newcommand{{\meDEC}}{{{me_dec:+.2f}}}
"""
with open("macros_fig7.tex", "w", encoding="utf-8") as f:
    f.write(macros)
```

@@

\begin{tabularx}{\paperwidth}{
  @{}
  >{\centering\arraybackslash}X
  >{\centering\arraybackslash}X
  @{}
}

% ---------- LIGNE 1 ----------
\textbf{\small JAN} \small ($r=\rJAN$,\, n=\nJAN,\, ME=\meJAN\%) &
\textbf{\small FEB} \small ($r=\rFEB$,\, n=\nFEB,\, ME=\meFEB\%) \\[-1mm]

\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_pluie_jan.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_pluie_fev.pdf} \\[1mm]

% ---------- LIGNE 2 ----------
\textbf{\small MAR} \small ($r=\rMAR$,\, n=\nMAR,\, ME=\meMAR\%) &
\textbf{\small APR} \small ($r=\rAPR$,\, n=\nAPR,\, ME=\meAPR\%) \\[-1mm]

\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_pluie_mar.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_pluie_avr.pdf} \\[1mm]

% ---------- LIGNE 3 ----------
\textbf{\small MAY} \small ($r=\rMAY$,\, n=\nMAY,\, ME=\meMAY\%) &
\textbf{\small JUN} \small ($r=\rJUN$,\, n=\nJUN,\, ME=\meJUN\%) \\[-1mm]

\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_pluie_mai.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_pluie_jui.pdf} \\[1mm]

% ---------- LIGNE 4 ----------
\textbf{\small JUL} \small ($r=\rJUL$,\, n=\nJUL,\, ME=\meJUL\%) &
\textbf{\small AUG} \small ($r=\rAUG$,\, n=\nAUG,\, ME=\meAUG\%) \\[-1mm]

\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_pluie_juill.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_pluie_aou.pdf} \\[1mm]

% ---------- LIGNE 5 ----------
\textbf{\small SEP} \small ($r=\rSEP$,\, n=\nSEP,\, ME=\meSEP\%) &
\textbf{\small OCT} \small ($r=\rOCT$,\, n=\nOCT,\, ME=\meOCT\%) \\[-1mm]

\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_pluie_sep.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_pluie_oct.pdf} \\[1mm]

% ---------- LIGNE 6 ----------
\textbf{\small NOV} \small ($r=\rNOV$,\, n=\nNOV,\, ME=\meNOV\%) &
\textbf{\small DEC} \small ($r=\rDEC$,\, n=\nDEC,\, ME=\meDEC\%) \\[-1mm]

\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_pluie_nov.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_pluie_dec.pdf} \\[1mm]

% ---------- LÉGENDE ----------
\mbox{\vspace{-2mm}} & \begin{minipage}[c]{\linewidth} \centering \makebox[0.85\linewidth][c]{\small \%} \includegraphics[width=0.85\linewidth,keepaspectratio]{../outputs/maps/gev_z_T_p/horaire/compare_12/sat_90.0/legend_horiz_signif.pdf}\vspace{-3mm} \end{minipage} \\

### 2025-11-24 article/fig_AROME_trend_saisons.qmd
Initial commit: src, article, outputs, outputs_nr10

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=0pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
  - \usepackage[export]{adjustbox}
---

@@

# trend_pluie_jan = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/jan/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_jan.svg",
# )
# trend_pluie_fev = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/fev/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_fev.svg",
# )
# trend_pluie_mar = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/mar/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_mar.svg",
# )
# trend_pluie_avr = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/avr/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_avr.svg",
# )
# trend_pluie_mai = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/mai/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_mai.svg",
# )
# trend_pluie_jui = assemble( # Juin, fichier FR "jui"
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/jui/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_jui.svg",
# )
# trend_pluie_juill = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/juill/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_juill.svg",
# )
# trend_pluie_aou = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/aou/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_aou.svg",
# )
# trend_pluie_sep = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/sep/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_sep.svg",
# )
# trend_pluie_oct = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/oct/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_oct.svg",
# )
# trend_pluie_nov = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/nov/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_nov.svg",
# )
# trend_pluie_dec = assemble(
# "../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/dec/mod_signif_norast.svg",
# "figures/trend_horaire_reduce_pluie_dec.svg",
# )
```

@@

\begin{tabularx}{\paperwidth}{
  >{\centering\arraybackslash}m{0.25\paperwidth}
  >{\centering\arraybackslash}m{0.25\paperwidth}
  >{\centering\arraybackslash}m{0.25\paperwidth}
  >{\centering\arraybackslash}m{0.25\paperwidth}
}

% ========== LIGNE 1 ==========

\textbf{\small JAN} &
\textbf{\small FEB} &
\textbf{\small MAR} &
\textbf{\small APR} \\[-1mm]

\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_reduce_pluie_jan.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_reduce_pluie_fev.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_reduce_pluie_mar.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_reduce_pluie_avr.pdf} \\[1mm]

% ========== LIGNE 2 ==========

\textbf{\small MAY} &
\textbf{\small JUN} &
\textbf{\small JUL} &
\textbf{\small AUG} \\[-1mm]

\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_reduce_pluie_mai.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_reduce_pluie_jui.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_reduce_pluie_juill.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_reduce_pluie_aou.pdf} \\[1mm]

% ========== LIGNE 3 ==========

\textbf{\small SEP} &
\textbf{\small OCT} &
\textbf{\small NOV} &
\textbf{\small DEC} \\[-1mm]

\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_reduce_pluie_sep.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_reduce_pluie_oct.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_reduce_pluie_nov.pdf} &
\includegraphics[width=\linewidth, trim=12 12 12 12, clip]{figures/trend_horaire_reduce_pluie_dec.pdf} \\[1mm]

% ---------- LÉGENDE ----------
\multicolumn{4}{c}{
  \begin{minipage}[c]{\paperwidth}
    \centering
    {\small \%} \\[0mm]
    \includegraphics[width=0.35\linewidth]{../outputs/maps/gev_z_T_p/horaire_reduce/compare_12/sat_90.0/legend_horiz_signif.pdf}
  \end{minipage}
} \\

\end{tabularx}

\vspace{0.75em}
\end{minipage}
\endgroup
```

>>>>

---
title: ""
format:
  pdf:
    listings: false
    documentclass: standalone
    classoption: ["border=0pt"]
    keep-tex: true
execute:
  echo: false
  warning: false
  message: false
header-includes:
  - \usepackage{graphicx}
  - \usepackage{tabularx}
  - \usepackage{array}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{caption}
---

@@

trend_horaire_reduce_pluie_hydro = assemble(
  "../outputs/maps/gev_z_T_p/horaire_reduce/compare_5/sat_90.0/hydro/mod_signif_norast.svg",
  "figures/trend_horaire_reduce_pluie_hydro.svg"
)
trend_horaire_reduce_pluie_ond = assemble(
  "../outputs/maps/gev_z_T_p/horaire_reduce/compare_5/sat_90.0/ond/mod_signif_norast.svg",
  "figures/trend_horaire_reduce_pluie_ond.svg"
)
trend_horaire_reduce_pluie_jfm = assemble(
  "../outputs/maps/gev_z_T_p/horaire_reduce/compare_5/sat_90.0/jfm/mod_signif_norast.svg",
  "figures/trend_horaire_reduce_pluie_jfm.svg"
)
trend_horaire_reduce_pluie_amj = assemble(
  "../outputs/maps/gev_z_T_p/horaire_reduce/compare_5/sat_90.0/amj/mod_signif_norast.svg",
  "figures/trend_horaire_reduce_pluie_amj.svg"
)
trend_horaire_reduce_pluie_jas = assemble(
  "../outputs/maps/gev_z_T_p/horaire_reduce/compare_5/sat_90.0/jas/mod_signif_norast.svg",
  "figures/trend_horaire_reduce_pluie_jas.svg"
)
```

@@

  \begin{tabularx}{\paperwidth}{
    >{\centering\arraybackslash}m{0.33\paperwidth}
    >{\centering\arraybackslash}m{0.33\paperwidth}
    >{\centering\arraybackslash}m{0.33\paperwidth}
  }

  % ===== Ligne 1 =====
  \textbf{\small OND} & \textbf{\small JFM} & \textbf{\small AMJ} \\[-0.5mm]
  \includegraphics[width=\linewidth]{figures/trend_horaire_reduce_pluie_ond.pdf} &
  \includegraphics[width=\linewidth]{figures/trend_horaire_reduce_pluie_jfm.pdf} &
  \includegraphics[width=\linewidth]{figures/trend_horaire_reduce_pluie_amj.pdf} \\

  % ===== Ligne 2 =====
  \textbf{\small JAS} & \textbf{\small YEAR} &  \\[-0.5mm]
  \includegraphics[width=\linewidth]{figures/trend_horaire_reduce_pluie_jas.pdf} &
  \includegraphics[width=\linewidth]{figures/trend_horaire_reduce_pluie_hydro.pdf} &
  \begin{minipage}[c]{\linewidth}
    \centering
    \includegraphics[width=0.9\linewidth]{../outputs/maps/gev_z_T_p/horaire_reduce/compare_5/sat_90.0/legend_horiz_signif.pdf}\\
    \small \%
  \end{minipage} \\

  \end{tabularx}
\end{minipage}
\endgroup
```
